Einschätzung zu den Befindlichkeiten der Wirtschaft in den Nachbarländern

### 2022-10-01 Paper_neighbour_countries_II.Rmd
commit, 1.10.22

#d <- filter(dat,indic %in% ty, geo == "IT", s_adj =="SA",time>="2010-01-01") 
d_hind_i <- filter(dat_hind_fac_i,indic %in% t, geo %in% cat, s_adj == "SA",time>="2016-01-01")

@@

d_hind_i$indic[d_hind_i$indic=="BS-FLP3-PC"] <- "Arbeitskräftemangel"
d_hind_i$indic[d_hind_i$indic=="BS-FLP5-PC"] <- "Andere"
d_hind_i$indic[d_hind_i$indic=="BS-FLP1-PC"] <- "Keine"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP2-PC"] <- "Insufficient Demand"

break.vec <- c(seq(from = min(d_hind_i$time), to = max(d_hind_i$time),
                   by = "16 month"),max(d_hind_i$time))

p <- ggplot(data = d_hind_i) + 
    geom_line(mapping = aes(x = time, y = values, color=indic),size=.6) + 
    scale_color_manual(values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    coord_fixed(ratio=20) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  scale_x_date(date_labels = "%b %y",breaks=break.vec) +
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +
     #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

@@

```{r}
x <- structure(c(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[1]),.Dim = c(5, 6), .Dimnames = structure(list(Actual = c("EU-19", "Deutschland","Frankreich","Italien","Österreich"), Predicted = c(format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%B"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%B"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%B"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%B"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%B"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%B"))), .Names = c("Actual", "Predicted")), class = "table")

@@

d_hind_s <- filter(dat_hind_fac_s,indic %in% t, geo %in% cat, s_adj == "SA",time>="2016-01-01")

@@

d_hind_s$indic[d_hind_s$indic=="BS-FLB3-PC"] <- "Arbeitskräftemangel"
d_hind_s$indic[d_hind_s$indic=="BS-FLB6-PC"] <- "Andere"
d_hind_s$indic[d_hind_s$indic=="BS-FLB1-PC"] <- "Keine"
#d_hind_s$indic[d_hind_s$indic=="BS-FLB2-PC"] <- "Insufficient Demand"

@@

>>>>

#d <- filter(dat,indic %in% ty, geo == "IT", s_adj =="SA",time>="2010-01-01") 
d_hind_i <- filter(dat_hind_fac_i,indic ==  "BS-FLP3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")

d_hind_i$time <- as.yearqtr(d_hind_i$time)

@@

d_hind_i$indic[d_hind_i$indic=="BS-FLP3-PC"] <- "Arbeitskräftemangel"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP5-PC"] <- "Andere"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP1-PC"] <- "Keine"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP2-PC"] <- "Insufficient Demand"

#break.vec <- c(seq(from = min(d_hind_i$time), to = max(d_hind_i$time),
#                   by = "16 month"),max(d_hind_i$time))

p <- ggplot(data = d_hind_i) + 
    geom_line(mapping = aes(x = time, y = values, color=indic),size=.6) + 
    scale_color_manual(values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=20) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  #scale_x_date(date_labels = "%b %y",breaks=break.vec) +
    zoo::scale_x_yearqtr(breaks = seq(from = min(d_hind_i$time), to = max(d_hind_i$time), by = 2),format = '%Y Q%q')+
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +
     #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

@@

```{r}
x <- structure(c(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[1]),.Dim = c(5, 6), .Dimnames = structure(list(Actual = c("EU-19", "Deutschland","Frankreich","Italien","Österreich"), Predicted = c(format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"))), .Names = c("Actual", "Predicted")), class = "table")

@@

d_hind_s <- filter(dat_hind_fac_s,indic =="BS-FLB3-PC", geo %in% cat, s_adj == "SA",time>="2019-01-01")

@@

d_hind_s$indic[d_hind_s$indic=="BS-FLB3-PC"] <- "Arbeitskräftemangel"
#d_hind_s$indic[d_hind_s$indic=="BS-FLB6-PC"] <- "Andere"
#d_hind_s$indic[d_hind_s$indic=="BS-FLB1-PC"] <- "Keine"

#d_hind_s$indic[d_hind_s$indic=="BS-FLB2-PC"] <- "Insufficient Demand"

@@

```{r plot321, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

dat_hind_fac_i <- get_eurostat(id="ei_bsin_q_r2") #Industry (quarterly: ei_bsin_q_r2)
dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Services (quarterly: ei_bsin_q_r2)

d_hind_i <- filter(dat_hind_fac_i,indic ==  "BS-FLP3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01") 
d_hind_s <- filter(dat_hind_fac_s,indic =="BS-FLB3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")

d_hind_i$time <- as.yearqtr(d_hind_i$time)
d_hind_s$time <- as.yearqtr(d_hind_s$time)

d_hind_i <- rename(d_hind_i,Industry=values)
d_hind_s <- rename(d_hind_s,Services=values)

d_hind_i <- d_hind_i %>% 
  select(time, geo, Industry)
d_hind_s <- d_hind_s %>% 
  select(time, geo, Services)

d_hind_both <- merge(d_hind_i,d_hind_s,by=c("time","geo"),all=TRUE)

d_hind_both <- pivot_longer(d_hind_both, cols = 3:4, names_to ="branches",
 values_to = "values")

d_hind_both$geo[d_hind_both$geo=="AT"] <- "Österreich"
d_hind_both$geo[d_hind_both$geo=="EA19"] <- "EU-19"
d_hind_both$geo[d_hind_both$geo=="DE"] <- "Deutschland"
d_hind_both$geo[d_hind_both$geo=="FR"] <- "Frankreich"
d_hind_both$geo[d_hind_both$geo=="IT"] <- "Italien"

d_hind_both$branches[d_hind_both$branches=="Industry"] <- "Industrie"
d_hind_both$branches[d_hind_both$branches=="Services"] <- "Dienstleistungen"

#d_hind_both$indic[d_hind_both$indic=="BS-FLP3-PC"] <- "Arbeitskräftemangel"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP5-PC"] <- "Andere"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP1-PC"] <- "Keine"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP2-PC"] <- "Insufficient Demand"

#break.vec <- c(seq(from = min(d_hind_i$time), to = max(d_hind_i$time),
#                   by = "16 month"),max(d_hind_i$time))

p <- ggplot(data = d_hind_both) + 
    geom_line(mapping = aes(x = time, y = values, color=branches),size=.6) + 
    scale_color_manual(values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=20) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  #scale_x_date(date_labels = "%b %y",breaks=break.vec) +
    zoo::scale_x_yearqtr(breaks = seq(from = min(d_hind_i$time), to = max(d_hind_i$time), by = 2),format = '%Y Q%q')+
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +
     #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_both.pdf')
print(p)
dev.off()

```
\begin{figure}[] \centering
\includegraphics[trim={0 0cm 0 0cm },clip,width=\textwidth]
{/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_both.pdf}
\caption{Hemmnisse Sektoren} 
\label{Inf_M_W}
\end{figure}

```{r plot2d, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

dat_hind <- get_eurostat(id="ei_bsbu_m_r2") #Industry (quarterly: ei_bsin_q_r2)

d <- filter(dat_hind,indic =="BS-FLBA4-PC", geo %in% cat, s_adj == "SA",time>="2019-01-01")

d$indic[d$indic=="BS-FLBA4-PC"] <- "Arbeitskräftemangel"

p <- ggplot(data = d) + 
    geom_line(mapping = aes(x = time, y = values),size=.6) + 
    scale_color_manual(values = c("#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=.2) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
 # scale_x_date(date_labels = "%YQ%q",breaks=break.vec) +
 # zoo::scale_x_yearqtr(limits = c(min(d_hind_s$time), max(d_hind_s$time)),format = '%Y Q%q')+
  scale_x_date(date_labels = "%b %y",breaks=break.vec) +
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +   #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hind_constr.pdf')
print(p)
dev.off()

```
\begin{figure}[] \centering
\includegraphics[trim={0 0cm 0 0cm },clip,width=\textwidth]
{/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hind_constr.pdf}
\caption{Hemmnisse Bausektor} 
\label{Inf_M_W}
\end{figure}
